Price of Anarchy for Mean Field Games

### 2018-07-09 PoA.tex
small changes

	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have: 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t,
	$$
	The limits $\bar{x}_t^{\infty,r,MFG}$ and $v_t^{\infty,r}$ are bounded over $[0,T]$. By the bounded convergence theorem, we obtain:
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty.
	\end{equation*}
	It can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), when $r\to \infty$, we have $ \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt \rightarrow 0$	and thus, $\displaystyle \lim_{r \to \infty} PoA = 1$. Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 \neq 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1\neq 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	For the case $\bar{b}_2 \to 0$, we have $\displaystyle \lambda \to \lambda^{0,\bar{b}_2} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$
	and 
	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} \neq 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold. Let's denote the limiting solutions by 
	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit:
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
   	Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{0,\bar{b}_2} \int_0^T \left( (u_t^{0,\bar{b}_2} - w_t^{0,\bar{b}_2})\cdot \bar{x}_t^{0,\bar{b}_2,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. By the explicit formula, $0<v_t<\infty$ for $t>0$ and $0 \leq w^{0,\bar{b}_2}_0 < \infty$, and thus,
	\begin{equation*}
    \begin{split}
	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 (\mathbb{E}(\xi))^2, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&>0 .       
    \end{split}
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1. $$

>>>>

	Moreover, since $\bar{x}_t^{MFG} = \mathbb{E}(\xi) \exp(\int_0^t (b_1 + \bar{b}_1 - B\cdot u_s)ds)$ and $v_t = Var(\xi)\exp(2\int_0^t (b_1 - B^\eta \eta_s) ds) + \sigma^2 \int_0^t \exp(2 \int_s^t (b_1 - B^\eta \eta_u) du) ds$, by the bounded convergence theorem we have for each $t \in [0,T]$: 
	$$	\bar{x}_t^{MFG} \xrightarrow[r\to \infty]{} \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{\infty,r,MFG},\qquad
	  v_t \xrightarrow[r\to \infty]{} Var(\xi)e^{2b_1t} + \sigma^2 \int_0^t e^{2 b_1 (t-s) } ds =: v^{\infty,r}_t,
	$$
	The limits $\bar{x}_t^{\infty,r,MFG}$ and $v_t^{\infty,r}$ are bounded over $[0,T]$. By the bounded convergence theorem, we obtain:
	\begin{equation*}
		\lim_{r \to \infty} \int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = \int_0^T (u^{\infty,r}_t- w^{\infty,r}_t)^2 (\bar{x}_t^{\infty,r,MFG})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \frac{(b_2 + \bar{b}_2)^2}{r + \bar{r}(1 - \bar{s})^2}\int_0^T (\Delta \bar{\eta}_t \cdot \bar{x}_t^{MFG})^2 dt = 0.
	\end{equation*}
	It can be shown that $w^{\infty,r}_0\geq0$ and $v^{\infty,r}_t >0$ for $t>0$. Hence,
	\begin{equation*}
		\lim_{r \to \infty} SC^{MKV} = \int_0^T (q+\bar{q}) v^{\infty,r}_t dt + (q_T + \bar{q}_T) v^{\infty,r}_T + w^{\infty,r}_0 (\mathbb{E}(\xi))^2 \  >0.
	\end{equation*}
	Therefore, from Proposition \ref{prop:diff_SC} and equation (\ref{eq:PoA_LQ}), we have $\displaystyle \lim_{r \to \infty} PoA = 1$. Idem, by replacing $\lambda^{\infty,r}$ with $\lambda^{\infty,\bar{r}}: = \frac{b_2}{b_2 + \bar{b}_2} (1 - \bar{s})$, we obtain $\displaystyle \lim_{\bar{r} \to \infty} PoA = 1$.

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $\bar{b}_1> 0$, then 
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1\qquad \text{and} \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.
	\end{equation*}
	\label{prop:b2bar}
\end{proposition}
\begin{proof}
	For the case $\bar{b}_2 \to 0$, we have $\displaystyle \lambda \to \lambda^{0,\bar{b}_2} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}$
	and 
	$$B \to B^{0,\bar{b}_2} := \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2} > 0,\ C^u \to C^{0,\bar{b}_2}_u >0 ,\ D^u \to D^{0,\bar{b}_2}_u \geq 0.$$
	Thus, the existence and uniqueness for solutions of the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}) associated with $u_t$ and $w_t$, respectively, in the limiting region $\bar{b}_2 \to 0$ still hold. Let's denote the limiting solutions by 
	$u^{0,\bar{b}_2}_t, w^{0,\bar{b}_2}_t$. By the bounded convergence theorem, the mean function $\bar{x}_t^{MFG}$ has the limit: (ToDo reference equation)
   	$$\lim_{\bar{b}_2 \to 0} \bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B^{0,\bar{b}_2}\cdot u^{0,\bar{b}_2}_t) dt} =: \bar{x}^{0,\bar{b}_2,MFG}_t.$$ 
   	By our assumption on $\bar{b}_1$, we have $A^u \neq A^w$ and thus, $u^{0,\bar{b}_2}_t\neq w^{0,\bar{b}_2}_t$ on a set of positive Lebesgue measure.
   	Thus, by the bounded convergence theorem and the assumption on $\xi$, we deduce
	$$ \lim_{\bar{b}_2 \to 0} \Delta SC = \frac{1}{2} B^{0,\bar{b}_2} \int_0^T \left( (u_t^{0,\bar{b}_2} - w_t^{0,\bar{b}_2})\cdot \bar{x}_t^{0,\bar{b}_2,MFG} \right)^2 dt \  > 0. $$
	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. By the explicit formula, $0<v_t<\infty$ for $t>0$ and $0 \leq w^{0,\bar{b}_2}_0 < \infty$, and thus,
	\begin{equation*}
    \begin{split}
	    \lim_{\bar{b}_2 \to 0}SC^{MKV} &= h_{var} + w^{0,\bar{b}_2}_0 (\mathbb{E}(\xi))^2, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&<\infty, \\
	    \lim_{\bar{b}_2 \to 0}SC^{MKV}&>0 .       
    \end{split}
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA =: PoA^{0,\bar{b}_2} > 1. $$
